Lunar Lander with Deep Reinforcement Learning

### 2019-07-01 project_2/paper/paper.tex
Fixing typo in README.md

    \section{Methods}
    \label{sec:methods}
    To investigate how the integrated agent that combines all described improvements perform, using Lunar Lander environment as test-bed, we propose 5 different experiments detailed below.

>>>>

    \section{Methods}
    \label{sec:methods}
    To investigate how the integrated agent that combines all described improvements perform, using Lunar Lander environment as test-bed, we propose 4 different experiments detailed below.
